---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# microinverterdata

<!-- badges: start -->

[![R-CMD-check](https://github.com/CamembR/microinverterdata/actions/workflows/R-CMD-check.yaml/badge.svg)](https://github.com/CamembR/microinverterdata/actions/workflows/R-CMD-check.yaml) [![CRAN status](https://www.r-pkg.org/badges/version/microinverterdata)](https://CRAN.R-project.org/package=microinverterdata) [![](https://cranlogs.r-pkg.org/badges/microinverterdata)](https://cran.r-project.org/package=microinverterdata)

<!-- badges: end -->

The goal of microinverterdata is to provide access to your local micro-inverter data.

## Installation

You can install the development version of {microinverterdata} from [GitHub](https://github.com/) with:

``` r
# install.packages("pak")
pak::pak("CamembR/microinverterdata")
```

## Example

This is a basic example to get inverter data for a single device:

```{r example}
library(microinverterdata)

## single micro-inverter device data
get_output_data(device_ip = "192.168.0.75")

```

The single device here includes 2 separated inverters. We get one row of data per inverter, i.e. per solar panel.

You can also use a vector of IP adresses for `device_ip`. Thus the command would run on all the inverters

```{r multiple_inverters}
## multiple inverters data
get_output_data(device_ip = c("192.168.0.75", "192.168.0.186"))

```

The packages also gives access to inverter information through `get_device_info()` and inverter internal alarms through `get_alarm()`.

## Inverter support and configuration

The package here requires minimal version and configuration for the supported inverters :

| Inverter Manufacturer | Inverter Model | Firmware version | Configuration |
|------------------|------------------|------------------|------------------|
| APSystems | EZ1 | ≥ 1.7.0 | [Continuous local mode](https://camembr.github.io/microinverterdata/articles/APSystems_devices.html) |
