---
title: "data_collection"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{data_collection}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
library(httptest2)
start_vignette("APSystems_devices")
```

```{r setup}
library(microinverterdata)
```

# Data Collection

For inverters that do not collect historical data, you may want to do this collection with R. 

Here are some ideas to achieve it. 


## Use `pins` storage

- Initialize the board dataset maned "inverter_data" (only once)
We can choose the most simpler board to be the local board
```{r}
library(pins)
board <- board_local()
if (!"inverter_data" %in% pin_list(board)) {
  initial_data <- tibble::tibble(
    date = lubridate::now(), get_output_data(c("192.168.0.175"))
    )
  board |> pin_write(initial_data, name = "inverter_data", versioned = TRUE)
}

```


- Read the {pins} local board content for dataset "inverter_data"
```{r}
history <- board |> pin_read("inverter_data")
```

- Read new data from the inverter and append it to the dataset : 

```{r}
new_data <- tibble::tibble(
  date = lubridate::now(), get_output_data(c("192.168.0.175"))
  )
board |> pin_write(rbind(history, new_data), name = "inverter_data", versioned = TRUE)

```

- look at recorded versions
```{r}
board |> pin_versions("inverter_data")
```
As we know the dynamic behavior, we can move that to a R script and run it on a regular basis with system tools like crontab for linux : 

```{bash}
crontab -l
```


```{r, include=FALSE}
end_vignette()
```
